DATA 621 - Business Analytics and Data Mining

### 2020-10-27 HW3/HW3_Final_AA.Rmd
:DOH:

df <- read.csv(paste0(urlRemote, pathGithub, fileTrain))
nobs <- dim(df)[[1]]
DT <- as.data.table(df)
eval <- read.csv(paste0(urlRemote, pathGithub, fileTest))
```

>>>>

df <- read.csv(paste0(urlRemote, pathGithub, fileTrain))
nobs <- dim(df)[[1]]
DT <- as.data.table(df)
DT[, target := factor(target)]
eval <- read.csv(paste0(urlRemote, pathGithub, fileTest))
```
